Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
read relaxation example again

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an
imposed electric field or a fluid flow in the far-field, the long-range
attraction pulls two vesicles together until their separation distance
is close to $\delta$. The L.-J.~type potential prohibits physical
contact between two membranes and instead keep them close to the
separation distance $\delta$.  In
Section~\ref{subsec:qflow_draining_times}, we compute the expected time
for the vesicles to reach an equilibrium configuration and compare the
analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
bending and adhesive energies.

\subsection{Effects of the adhesion parameters on draining times}
\label{subsec:qflow_draining_times}
When two vesicles move towards (or away from) each other under a
constant force $F$ without any external fluid flow, the height $(h)$ of
the thin liquid film between two vesicles follows the draining
dynamics~\cite{RamachandranLeal2010_PoF}
\begin{align}
  \label{eq:dhdt}
  \frac{d h}{dt} \sim \frac{K_a^{2/3} F^{1/3}}{\mu R_0^{10/3}} h^3,
\end{align}
where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of the
exterior fluid, and $R_0$ is the radius of the undeformed vesicle.  For
the case of a constant forcing $F$ (independent of separation distance
$h$ and time $t$), equation~\eqref{eq:dhdt} can be easily integrated to
relate the film thickness $h$ and time $t$:
\begin{align*}
  t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}
    \frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
\end{align*}
where $h(0)$ is the vesicle separation at $t=0$.  We note that $F< (>)
0$ for an attractive  (repulsive) interaction between two vesicles,  and
consequently $h(t)$ decreases (increases) from  the initial separation
distance $h(0)$.  When the force is attractive, $h$ decreases
monotonically, and $t$ in the above equation is the draining time that
diverges as $h\rightarrow 0$.

When the force on each vesicle is a function of the separation distance
$h$ of the form (with integers $n>m\ge 2$)
\begin{align}
  \label{eq:Fh}
  F(h) \sim \mathcal{H} \frac{\delta^m}{h^{m+1}}
    \left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
\end{align}
attraction is dominant at ``large" distances ($h > \delta$) while
repulsion is dominant at ``small" distances ($h<\delta$).  Integration
of equation~\eqref{eq:dhdt} with the $F(h)$ as defined in
equation~\eqref{eq:Fh} gives the relationship between $t$ and $h$.  In
this case the relationship involves an integral of a function of
dimensionless $\bar{h} \equiv h/\delta$:
\begin{align*}
  t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = 
    \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = 
    -\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
      \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}},
\end{align*}
Solving for $t$,
\begin{align}
\label{eq:teq_scaling}
  t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}},
\end{align}
and equation~\eqref{eq:teq_scaling} tells us that both the adhesion
strength $\mathcal{H}$ and the separation distance $\delta$ affect the
time it takes for a pair of vesicles to reach the separation distance
$\delta$ under adhesion force $F$ in equation~\eqref{eq:Fh}.  In
particular, the duration $t$ is proportional to (i) the separation
distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as
$\delta\rightarrow 0$), and (ii) the adhesion strength
$\mathcal{H}^{-1/3}$ (as in constant forcing
case~\cite{RamachandranLeal2010_PoF}).  From the above analysis we also
expect that the scaling of $t$ with respect to $\delta$ depends on the
adhesion potential, while the scaling with respect to adhesion strength
is independent of the specific form of the potential.

@@

To test the scaling of the duration $t$ with respect to $\mathcal{H}$
and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent
flow.  Starting with two vesicles at a distance of twice the vesicle
radius at $t=0$, the long-range attraction pulls the vesicles together.
The left plot of Figure~\ref{fig:qflow00} shows the scaled adhesion
energy versus time with $\mathcal{H}=0.1$ and three values of $\delta$
as labeled.  Adhesion energy reaches minimum at equilibrium, and the
scaled $E_{adh}$ evolves towards zero at equilibrium.  The arrows
indicate the times when the scaled adhesion energy reaches within $1\%$
of equilibrium: $t\sim 96$ for $\delta=0.2$, $t\sim 45$ for $\delta =
0.3$, and $t\sim 30$ for $\delta=0.4$:
\begin{align*}
\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 
  &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 
  &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
\end{align*}

@@

\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} 
We next simulate a pair of identical two-dimensional vesicles
interacting with each other via the adhesion force in
equation~\eqref{eq:Fh}.  The initial vesicle placement is smaller than
in the previous simulations so that the equilibrium configuration is
achieved with a shorter time horizon.  Once a vesicle doublet is
formed, the membrane shape in the contact region depends on the adhesion
strength relative to the membrane bending rigidity.  For weak to
moderate adhesion strength, vesicle membranes are flattened in the
contact region while the rest of vesicle maintains a nearly spherical
shape~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape  that has been observed in RBC doublet as
well~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of
  a doublet of identical vesicles under adhesion in a quiescent flow.
  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$ are labeled.
  The color coding is the tension along the vesicle.  Vesicle length is
  fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$,
  $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}: Overall equilibrium
  shapes of two vesicles under adhesive interactions vary with reduced
  area.  {\em Right}: Membrane shapes in the contact region.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L.-J. potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the 
vesicle membrane on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom on the
membranes in the contact region, where the membranes are not perfectly
flat: For all values of reduced area we observe that membranes are
slightly curved with a dip at the edge.  Such membrane undulation in the
contact region is predicted by lubrication analyses on a membrane
under adhesion with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
YoungStone2017_PRF}.  Also the dip at the edge of contact region is
related to but different from the buckling of membrane under strong
adhesion: A closer inspection on the dip at the edge shows that the
membrane distance is smaller than the neutral separation distance
$\delta$ there. Thus the adhesion force is attractive for most of the
membranes in the contact region except at the edge, where the adhesive
force turns repulsive.  Results from the lubrication analysis shows that
this dip and slightly curved shape in the contact region are independent
of the adhesion strength. The high membrane curvature at the edge may
pose a problem for using the contact angle there to estimate the
adhesion strength. This inspires us to investigate the possibility of
using a dynamic fluid trap to measure the adhesion strength (see
Section~\ref{sec:eflow}).

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}:
  Total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
  of two energies plotted against reduced area $\Delta A$. Two vesicles in the doublet are of the same length, reduced area
  and bending rigidity modulus ($\kappa=1$) with $\mathcal{H}=5$ and $\delta=0.2$.}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
  \caption{\label{fig:Dec18_equilibrium} 
  Total bending energy ({\em left}) and adhesion energy ({\em right}) of
  a vesicle doublet at equilibrium versus the adhesion strength
  $\mathcal{H}$.  The two vesicles in the doublet have the same length
  and reduced area $\Delta A=0.95$, with separation distance $\delta =
  0.2$ (triangles), $0.3$ (crosses), and $0.4$ (circles).}
\end{figure}

Figure~\ref{fig:Dec18_equilibrium} demonstrates how the adhesion
strength $\mathcal{H}$ and separation distance $\delta$ affect the
equilibrium configuration of two vesicles under adhesive interactions.
For both vesicles the reduced area $\Delta A=0.95$ and the bending
rigidity is $\kappa_b = 1$.  The total bending (left) and adhesion
(right) energies at equilibrium are plotted against $\mathcal{H}$ for
three values of separation distance $\delta$.  We observe that for
$\Delta A=0.95$ the equilibrium vesicle shape does not vary much with
the adhesion strength $\mathcal{H}$, while the total adhesion energy
varies linearly with $\mathcal{H}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an
imposed electric field or a fluid flow in the far-field, the long-range
attraction pulls the vesicles together until their separation distance
is close to $\delta$. The L.-J.~type potential prohibits physical
contact between the two membranes and instead keeps them close to the
separation distance $\delta$.  In
Section~\ref{subsec:qflow_draining_times}, we compute the expected time
for the vesicles to reach an equilibrium configuration and compare the
analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
shape of the contact region and the bending and adhesive energies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of the adhesion parameters on draining times}
\label{subsec:qflow_draining_times}
When two vesicles move towards (or away from) each other under a
constant force $F$ without any external fluid flow, the height, $h$, of
the thin liquid film between two vesicles follows the draining
dynamics~\cite{RamachandranLeal2010_PoF}
\begin{align}
  \label{eq:dhdt}
  \frac{d h}{dt} \sim \frac{K_a^{2/3} F^{1/3}}{\mu R_0^{10/3}} h^3,
\end{align}
where $K_a$ is the area expansion modulus, $\mu$ is the viscosity of the
exterior fluid, and $R_0$ is the radius of the undeformed vesicle.  For
the case of a constant forcing $F$ (independent of separation distance
$h$ and time $t$), equation~\eqref{eq:dhdt} can be easily integrated to
relate the film thickness $h$ and time $t$:
\begin{align*}
  t \sim \frac{\mu R_0^{10/3}}{K_a^{2/3} F^{1/3}}
    \frac{1}{2 h^2} \bigg|^{h(t)}_{h(0)},
\end{align*}
where $h(0)$ is the vesicle separation at $t=0$.  We note that $F< (>)
0$ for an attractive  (repulsive) interaction between two vesicles,  and
consequently $h(t)$ decreases (increases) from  the initial separation
distance $h(0)$.  When the force is attractive, $h$ decreases
monotonically, and $t$ in the above equation is the draining time that
diverges as $h\rightarrow 0$.

When the force on each vesicle is a function of the separation distance
$h$ of the form
\begin{align}
  \label{eq:Fh}
  F(h) \sim \mathcal{H} \frac{\delta^m}{h^{m+1}}
    \left(\left(\frac{\delta}{h}\right)^{m-n}-1\right),
\end{align}
with $n>m\ge 2$ being integers, attraction is dominant at ``large"
distances ($h > \delta$) while repulsion is dominant at ``small"
distances ($h<\delta$).  Integration of equation~\eqref{eq:dhdt} with
the $F(h)$ as defined in equation~\eqref{eq:Fh} gives the relationship
between $t$ and $h$.  In this case, the relationship involves an
integral of a function of the dimensionless variable $\bar{h} \equiv
h/\delta$:
\begin{align*}
  t\frac{K_a^{2/3}}{\mu R_0^{10/3}}& = 
    \int^{h(t)}_{h(0)}-\frac{dh}{h^3 F^{1/3}} = 
    -\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}}\int^{\bar{h}(t)}_{\bar{h}(0)}
      \frac{d \bar{h}}{\bar{h}^{(8-m)/3}(\bar{h}^{m-n}-1)^{1/3}}.
\end{align*}
Solving for $t$,
\begin{align}
\label{eq:teq_scaling}
  t\sim \frac{\mu R_0^{10/3}}{K_a^{2/3}}\frac{1}{\mathcal{H}^{1/3}\delta^{5/3}},
\end{align}
and equation~\eqref{eq:teq_scaling} tells us that both the adhesion
strength $\mathcal{H}$ and the separation distance $\delta$ affect the
time it takes for a pair of vesicles to reach the separation distance
$\delta$ under adhesion force $F$ in equation~\eqref{eq:Fh}.  In
particular, the duration $t$ is proportional to (i) the separation
distance $\delta^{-5/3}$ (thus $t\rightarrow \infty$ as
$\delta\rightarrow 0$), and (ii) the adhesion strength
$\mathcal{H}^{-1/3}$ (as in the constant forcing
case~\cite{RamachandranLeal2010_PoF}).  From the above analysis we also
expect that the scaling of $t$ with respect to $\delta$ depends on the
adhesion potential, while the scaling with respect to adhesion strength
is independent of the specific form of the potential.

@@

To test the scaling of the duration $t$ with respect to $\mathcal{H}$
and $\delta$, we simulate the vesicle adhesion dynamics in a quiescent
flow.  Starting with two vesicles at a distance of twice the vesicle
radius, the long-range attraction pulls the vesicles together.  The left
plot of Figure~\ref{fig:qflow00} shows the scaled adhesion energy versus
time with $\mathcal{H}=0.1$ and three values of $\delta$ as labeled.
Adhesion energy reaches minimum at equilibrium, and the scaled $E_{adh}$
evolves towards zero at equilibrium.  The arrows indicate the times when
the scaled adhesion energy reaches within $1\%$ of equilibrium: $t\sim
96$ for $\delta=0.2$, $t\sim 45$ for $\delta = 0.3$, and $t\sim 30$ for
$\delta=0.4$:
\begin{align*}
\frac{t_{\delta=0.2}}{t_{\delta=0.4}} \sim \frac{96}{30}=3.2 
  &\Longleftrightarrow \left(\frac{0.4}{0.2}\right)^{5/3}\sim 3.17,\\
\frac{t_{\delta=0.2}}{t_{\delta=0.3}} \sim \frac{96}{45}=2.1 
  &\Longleftrightarrow \left(\frac{0.3}{0.2}\right)^{5/3}\sim 2.
\end{align*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Effects of the adhesion parameters on equilibrium
configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} We again simulate two identical
adhering vesicles with the adhesion force in equation~\eqref{eq:Fh}.
The initial vesicle separation is smaller than in the previous
simulations so that the equilibrium configuration is achieved in a
shorter time horizon.  Once a vesicle doublet is formed, the membrane
shape in the contact region depends on the adhesion strength relative to
the membrane bending rigidity.  For weak to moderate adhesion strength,
vesicle membranes are flattened in the contact region while the rest of
vesicle maintains a nearly spherical shape~\cite{EvansMetcalfe1984_BJ,
Book_PhysicalBasisCellAdhesion, Book_IntermolecularSurfaceForces,
RamachandranAndersonLealIsraelachvili2010_Langmuir}.  Under a strong
adhesion, however, the vesicle membranes in the contact region buckle
and form a sigmoidal shape that has also been observed in RBC
doublets~\cite{Ziherl2007_PRL, ZiherlSvetina2007_PNAS,
FlormannAouane2017_SciReports}.  An external electric field is also able
to buckle a vesicle membrane that is adhered to a solid
substrate~\cite{SteinkuhlerAgudo-Canalejo2016_BJ}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} The equilibrium configuration
  of a doublet of identical vesicles under adhesion in a quiescent flow.
  The vesicle reduced areas of $\Delta A=0.95$, $0.75$, and $0.6$ are
  labeled.  The color coding is the tension along the vesicle.  The
  vesicle length is fixed at $2\pi$, the dimensionless bending rigidity
  modulus is $\kappa_b=1$, the Hamaker constant is $\mathcal{H}=5$, and
  the separation distance is $\delta=0.2$.  {\em Left}: The overall
  equilibrium shapes of two vesicles under adhesive interactions vary
  with the reduced area.  {\em Right}: The membrane shapes in the
  contact region.} 
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a $(m,n) = (12,6)$
L.-J.~potential~\cite{FlormannAouane2017_SciReports}.  As the reduced
area decreases further, we observe undulation of the vesicle membrane on
the non-contact side while the contact region remains flat.  The color
coding along each curve is the tension of the vesicle membrane.  We
observe that the membrane tension in the contact region is very
negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

The right plot of Figure~\ref{fig:Dec18_vesicle_shape} is a zoom on the
membranes in the contact region, where the membranes are not perfectly
flat---at all reduced area we observe that the membranes are slightly
curved with a dip at the edge.  Such membrane undulation in the contact
region is predicted by lubrication analyses on a membrane under adhesion
with a solid substrate~\cite{BlountMiksisDavis2013_PRSa,
YoungStone2017_PRF}.  Also the dip at the edge of contact region is
related to but different from the buckling of membrane under strong
adhesion: A closer inspection on the dip at the edge shows that the
membrane distance is smaller than the neutral separation distance
$\delta$ there. Thus the adhesion force is attractive for most of the
membranes in the contact region except at the edge, where the adhesive
force turns repulsive.  Results from the lubrication analysis show that
this dip and slightly curved shape in the contact region are independent
of the adhesion strength. The high membrane curvature at the edge may
pose a problem for using the contact angle there to estimate the
adhesion strength. This inspires us to investigate the possibility of
using a dynamic fluid trap to measure the adhesion strength (see
Section~\ref{sec:eflow}).

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}: The
  total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: The
  sum of two energies plotted against reduced area $\Delta A$. The two
  vesicles in the doublet are of the same length and reduced area.  The
  Hamaker constant is $\mathcal{H} = 5$ and the separation distance is
  $\delta = 0.2$.}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
  \caption{\label{fig:Dec18_equilibrium} 
  The total bending energy ({\em left}) and adhesion energy ({\em
  right}) of a vesicle doublet at equilibrium versus the adhesion
  strength $\mathcal{H}$.  The two identical vesicles in the doublet
  have a length of $2\pi$ and a reduced area of $\Delta A=0.95$, with
  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
  $0.4$ (circles).}
\end{figure}

Figure~\ref{fig:Dec18_equilibrium} demonstrates how the adhesion
strength $\mathcal{H}$ and separation distance $\delta$ affect the
equilibrium configuration of two vesicles under adhesive interactions.
Both vesicles have a length of $2\pi$ and a reduced area of $\Delta A =
0.95$.  The total bending (left) and adhesion (right) energies at
equilibrium are plotted against $\mathcal{H}$ for three values of the
separation distance $\delta$.  We observe that for $\Delta A=0.95$ the
equilibrium vesicle shape does not vary much with the adhesion strength
$\mathcal{H}$, while the total adhesion energy varies linearly with
$\mathcal{H}$.
